2.6: Inferential Statistics I

### 2019-10-03 static/slides/12-slides.Rmd
Fix p-value definition!

$$p(\delta_i \geq \delta^*|H_0 \text{ is true})$$
  - where $\delta$ represents some test statistic
  - $\delta_i$ is the test statistic we observe in our sample
  - $\delta^*$ is some **critical value** of the test statistic
  - More on this in a bit

>>>>

$$p(\delta \geq \delta_i|H_0 \text{ is true})$$
  - where $\delta$ represents some test statistic
  - $\delta_i$ is the test statistic we observe in our sample
  - More on this in a bit
